---
title: 'Experiment 1 - analysis'
author: 'Didino Daniele'
date: 'October 2021'
output: 
  html_document:
    code_folding: hide
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(
  comment = '#>',
  collapse = TRUE,
  echo = TRUE)
```

This file is part of the supplementary material of the manuscript:
Didino, D., Brandtner, M., & Knops, A. (2021). No influence of masked priming 
on the multiplication fact retrieval in a result verification task.

This script reports the analysis for experiment 1.

Dataset loaded: **exp1_data.rds** (data of *result verification task*)

Load libraries, my functions (**my_functions** folder) and data 
(**data/processed** folder):

```{r}
library('ggpubr')
library('here')
library('kableExtra')
# library('knitr')
library('plotly')
library('ggridges')
library('tidyverse')
library('BayesFactor')

# Load my functions
source(here('funcs', 'load_my_functions.R'))

# Load data
exp1 <- readRDS(here('data', 'processed', 'exp1_data.rds'))
```


Exclude outliers

```{r}
exp1 <- 
  exp1 %>% 
  filter(outlier == FALSE)
```


# RTs plots

RTs distribution across prime conditions:

```{r, fig.height = 6, fig.width = 8, fig.align = 'center'}
plot_1 <-
  exp1 %>% 
  ggplot(aes(RT, fill = prime_cond)) +
  geom_density(alpha = 0.6) +
  facet_wrap(~ problem_size, ncol = 2) 

ggplotly(plot_1)
```


Comparison between the distribution of the RTs of the neutral condition and the
other conditions. The neutral condition is replicated next to each condition to
facilitate the comparison.

```{r, fig.height = 6, fig.width = 9, fig.align = 'center'}
exp1_rainplot <- 
  exp1 %>% 
  return_means(RT, c('problem_size', 'sj', 'prime_cond'), .) %>% 
  return_df_plot(problem_size,
                 prime_cond,
                 'neutral')

# Set H0/H1 position
segs <- 
  tribble(
    ~problem_size, ~cond,       ~neutral,        ~lab, ~ys,
    'Large',       'identity',  'Neutral', 'H1', 950,
    'Large',       'neigh_inc', 'Neutral', 'H1', 950,
    'Large',       'unrel_con', 'Neutral', 'H0', 950,
    'Large',       'unrel_inc', 'Neutral', 'H1', 950,
    'Small',       'identity',  'Neutral', 'H1', 950,
    'Small',       'neigh_inc', 'Neutral', 'H1', 950,
    'Small',       'unrel_con', 'Neutral', 'H1', 950,
    'Small',       'unrel_inc', 'Neutral', 'H1', 950)

# Plot
prime_plot <- 
 list(exp1_RT_distr =
        exp1_rainplot %>% 
        mutate(
          neutral = if_else(neutral == 'neutral', 'Neutral', 'Other'),
          problem_size = if_else(problem_size == 'large', 'Large', 'Small')
          ) %>% 
        ggplot(aes(x = cond, y = DV, fill = neutral)) +
        geom_flat_violin(aes(fill = neutral),
                         position = position_nudge(x = 0.18, y = 0),
                         adjust = 1.5,
                         trim = FALSE,
                         alpha = .5,
                         colour = NA) +
        geom_point(aes(x = as.numeric(factor(cond)) - 0.23, y = DV, colour = neutral),
                   position = position_jitter(width = 0.05, height = 0),
                   size = 1,
                   shape = 20) +
        geom_boxplot(aes(x = cond, y = DV, fill = neutral),
                     outlier.shape = NA,
                     alpha = 0.5,
                     width = 0.3,
                     colour = 'black') +
        geom_text(data = segs,
                  aes(x = cond,  y = ys, label = lab),
                  size = 3.5) + 
        geom_vline(xintercept = c(c(0:3) + 1.65),
                   linetype = 'solid',
                   color = 'grey80',
                   size = 0.3) +
        # scale_colour_brewer(palette = 'Dark2') +
        # scale_fill_brewer(palette = 'Dark2') +
        labs(x = 'Prime condition', y = 'RTs') +
        facet_wrap(~ problem_size, ncol = 1, strip.position = 'right') +
        theme(
          #panel.grid.major = element_blank(),
          #panel.grid.minor = element_blank(),
          panel.background = element_blank(),
          panel.grid.major.y = element_line(colour = 'grey90'),
          panel.grid.minor.y = element_line(colour = 'grey90'),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          legend.title = element_blank(),
          strip.background = element_blank(),
          text = element_text(size = 15),
          axis.text = element_text(size = 12, colour = 'black'),
          axis.text.x = element_text(angle = 45, hjust = 1),
          # axis.title = element_text(size = 14),
          panel.border = element_rect(colour = 'black', fill = NA, size = 0.5)
        )
 )

# show plot
prime_plot$exp1_RT_distr
```


```{r}
# Plot - Black and white version
prime_plot$exp1_RT_distr_bw <- 
  exp1_rainplot %>% 
  mutate(
    neutral = if_else(neutral == 'neutral', 'Neutral', 'Other'),
    problem_size = if_else(problem_size == 'large', 'Large', 'Small')
    ) %>% 
  ggplot(aes(x = cond, y = DV, fill = neutral)) +
  geom_flat_violin(position = position_nudge(x = 0.15, y = 0),
                   adjust = 1.5,
                   trim = FALSE,
                   alpha = .5,
                   colour = 'black') +
  geom_point(aes(x = as.numeric(factor(cond)) - 0.2, y = DV),
             position = position_jitter(width = 0.05, height = 0),
             size = 1,
             shape = 21) +
  geom_boxplot(outlier.shape = NA,
               alpha = 0.5,
               width = 0.25) +
  geom_text(data = segs,
            aes(x = cond,  y = ys, label = lab),
            size = 3.5) + 
  geom_vline(xintercept = c(c(0:3) + 1.65),
             linetype = 'solid',
             color = 'grey80',
             size = 0.3) +
  scale_fill_manual(values = c('white', 'grey20')) +
  scale_color_manual(values = c('white', 'grey20')) +
  labs(x = 'Prime condition', y = 'RTs') +
  facet_wrap(~ problem_size, ncol = 1, strip.position = 'right') +
  theme(
    #panel.grid.major = element_blank(),
    #panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    panel.grid.major.y = element_line(colour = 'grey90'),
    panel.grid.minor.y = element_line(colour = 'grey90'),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    legend.title = element_blank(),
    strip.background = element_blank(),
    text = element_text(size = 15),
    axis.text = element_text(size = 12, colour = 'black'),
    axis.text.x = element_text(angle = 45, hjust = 1),
    # axis.title = element_text(size = 14),
    panel.border = element_rect(colour = 'black', fill = NA, size = 0.5)
  )
```


# Bayes factor

Bayes factors are computer with the package **BayesFactor**.

```{r}
tribble(
  ~BF,      ~Evidence,
  '0-3',    'Anectodal',
  '3-10',   'Moderate',
  '10-30',  'Strong',
  '30-100', 'Very_strong',
  '>100',   'Decisive') %>% 
   make_table('Bayes factor interpretation')
```

Compute Bayes factors

```{r}
exp1_bf <- 
  exp1 %>% 
  return_BF_ttest(problem_size,
                  prime_cond,
                  'neutral',
                  RT,
                  ID = 'sj')

exp1_bf

exp1_bf <- 
  exp1_bf %>%
  select(problem_size, prime_cond.x, bf) %>% 
  rename(prime_cond = prime_cond.x, BF_10 = bf) %>% 
  mutate(
    BF_01 = 1 / BF_10
  ) 

# # Print results in a file
# exp1_bf %>% 
#   mutate(across(where(is.numeric), ~round(.x, digits = 2))) %>% 
#   print_result('exp1_BF')
# 
# # Show results
# exp1_bf %>% 
#   make_table('Bayes factor')
```


Calculate statistics for RT

```{r}
# Calculate statistics
exp1_stats <- 
  exp1 %>%
  return_stats(c('problem_size', 'prime_cond'))

# Add difference between prime means and neutral prime mean
exp1_stats <- 
  left_join(
    exp1_stats,
    exp1_stats %>% 
      filter(prime_cond == 'neutral') %>% 
      select(problem_size, Mean) %>% 
      rename(Diff = Mean)
  ) %>% 
  mutate(
    Diff = Mean - Diff
  )

# # Print results in a file
# exp1_stats %>% 
#   mutate(across(where(is.numeric), round)) %>% 
#   print_result('exp1_stats_RTs')
# 
# # Show results
# exp1_stats %>% 
#    make_table('Statistics (prime condition by problem size)')
```



# Table 1

Table with RTs mean, standard deviation and standard error (aggregated on 
subject and condition), and Bayes factors:

```{r}
exp1_table <- 
  full_join(
    exp1_stats %>% 
      mutate(across(where(is.numeric), ~round(.x, digits = 0))),
    exp1_bf %>% 
      mutate(across(where(is.numeric), ~round(.x, digits = 2))))

# Print results in a file
exp1_table %>% 
  # mutate(across(where(is.numeric), ~round(.x, digits = 2))) %>% 
  print_result('exp1_table')

# Show results
exp1_table %>% 
   make_table('Table1')
```


### Plot prime conditions

```{r, fig.height = 6, fig.width = 5, fig.align = 'center'}
# Set bar colors ("neutral" is the 4th and the 10th)
bar_colors <- c('gray80', 'gray80', 'gray80', 'gray40', 'gray80', 'gray80',
                'gray80', 'gray80', 'gray80', 'gray40', 'gray80', 'gray80')

# Set H0/H1 position
segs <- 
  tribble(
    ~problem_size, ~prime_cond, ~lab, ~ys,
     'large',      'identity',  'H1', 510,
     'large',      'neigh_inc', 'H1', 510,
     'large',      'unrel_con', 'H0', 510,
     'large',      'unrel_inc', 'H1', 510,
     'small',      'identity',  'H1', 540,
     'small',      'neigh_inc', 'H1', 510,
     'small',      'unrel_con', 'H1', 510,
     'small',      'unrel_inc', 'H1', 510)

# plot prime type
prime_plot$exp1_box <- 
  exp1_stats %>% 
  mutate(
    prime_cond = factor(
      prime_cond,
      levels = c('identity', 'neutral', 'neigh_con', 'neigh_inc', 'unrel_con', 'unrel_inc')
  )) %>% 
  ggplot(aes(x = prime_cond, y = Mean, fill = prime_cond)) +
  geom_bar(stat = 'identity',
           fill = bar_colors,
           width = 0.6,
           show.legend = FALSE) +
  geom_errorbar(
    aes(group = prime_cond, ymin = Mean - SE, ymax = Mean + SE),
    width = 0.07,
    position = position_dodge(0.9)) +
  geom_text(data = segs,
            aes(x = prime_cond,  y = ys, label = lab),
            size = 3) +
  coord_cartesian(ylim = c(500, 675)) +
  labs(x = 'Prime cond', y = 'Mean RTs') +
  facet_wrap(~problem_size, ncol = 1) +
  theme(
    # panel.grid.major = element_blank(),
    # panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    panel.grid.major.y = element_line(colour = 'grey90'),
    panel.grid.minor.y = element_line(colour = 'grey90'),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    text = element_text(size = 15),
    axis.text = element_text(size = 12, colour = 'black'),
    axis.text.x = element_text(angle = 45, hjust = 1),
    # axis.title = element_text(size = 14),
    panel.border = element_rect(colour = 'black', fill = NA, size = 0.5))

# show plot
prime_plot$exp1_box
```



### Plot Bayes factors

```{r, fig.height = 6, fig.width = 5, fig.align = 'center'}
# Set asterisk position
segs <- 
  tribble(
    ~problem_size, ~prime_cond, ~lab,    ~ys,
     'large',      'identity',   '>100',  95,
     'large',      'neigh_con',  '',      95,
     'large',      'neigh_inc',  '>100',  95,
     'large',      'unrel_con',  '',      95,
     'large',      'unrel_inc',  '',      95,
     'small',      'identity',   '>100',  95,
     'small',      'neigh_con',  '',      95,
     'small',      'neigh_inc',  '',      95,
     'small',      'unrel_con',  '>100',  95,
     'small',      'unrel_inc',  '',      95,
  )

# plot prime type
prime_plot$exp1_bf <- 
  exp1_bf %>% 
  mutate(
    prime_cond = factor(
      prime_cond,
      levels = c('identity', 'neigh_con', 'neigh_inc', 'unrel_con', 'unrel_inc')),
    BF_10 = case_when(
      BF_10	> 100 ~ 100,
      TRUE ~ BF_10
    )
  ) %>% 
  ggplot(aes(x = prime_cond, y = BF_10, fill = prime_cond)) +
  geom_bar(stat = 'identity',
           fill = 'gray80',
           width = 0.6,
           show.legend = FALSE) +
  geom_text(data = segs,
                  aes(x = prime_cond,  y = ys, label = lab),
                  size = 3) +
  geom_hline(yintercept = c(3, 10, 30, 100),
             linetype = 'dashed',
             color = 'red',
             size = 0.5) +
  coord_cartesian(ylim = c(0, 100)) +
  labs(x = 'Prime cond', y = bquote('Bayes factor (' ~BF[10]~ ')')) +
  facet_wrap(~problem_size, ncol = 1) +
  theme(
    #panel.grid.major = element_blank(),
    #panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    panel.grid.major.y = element_line(colour = 'grey90'),
    panel.grid.minor.y = element_line(colour = 'grey90'),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    text = element_text(size = 15),
    axis.text = element_text(size = 12, colour = 'black'),
    axis.text.x = element_text(angle = 45, hjust = 1),
    # axis.title = element_text(size = 14),
    panel.border = element_rect(colour = 'black', fill = NA, size = 0.5))
  NULL

# show plot
prime_plot$exp1_bf
```


# Frequentist t-tests 


Calculate the t-tests between neutral prime and other conditions (the results 
are also saved in the folder **results**)

```{r}
# prepare conditions to compare in the t-tests
prime_cond_to_comprare <- 
  list(c('identity', 'neutral'),
       c('neigh_con', 'neutral'),
       c('neigh_inc', 'neutral'),
       c('unrel_con', 'neutral'),
       c('unrel_inc', 'neutral'))


# t-tests between prime conditions
exp1_ttests <- 
  exp1 %>% 
  group_by(problem_size) %>% 
  group_nest() %>% 
  mutate(
    ttests = map(
      data,
      ~return_ttest_2samples(RT,
                             prime_cond,
                             prime_cond_to_comprare,
                             c('sj', 'prime_cond'),
                             .)
  )) %>% 
  select(problem_size, ttests) %>% 
  unnest(ttests) %>% 
  mutate(
    p_adj = p.adjust(p, method = 'holm'),
    Sig_adj = p.adjust(p, method = 'holm') < 0.05
  )

# Print the results in csv and txt files
exp1_ttests %>% 
  print_result(., 'exp1_ttests')

# Show the table with the statistics
exp1_ttests %>%
  make_table('T-tests for experiment 1')
```


# Save plots in a file

```{r, fig.show='hide'}
ggarrange(prime_plot$exp1_RT_distr)
ggsave(here('figures', 'exp1_RTs_distr.tiff'),
       width = 9,
       height = 5,
       dpi = 150) # or dpi = 300

ggarrange(prime_plot$exp1_RT_distr_bw)
ggsave(here('figures', 'exp1_RTs_distr_bw.tiff'),
       width = 9,
       height = 5,
       dpi = 150) # or dpi = 300

ggarrange(prime_plot$exp1_box)
ggsave(here('figures', 'exp1_RTs.tiff'),
       width = 8,
       height = 6,
       dpi = 150) # or dpi = 300

ggarrange(prime_plot$exp1_bf)
ggsave(here('figures', 'exp1_BF.tiff'),
       width = 8,
       height = 6,
       dpi = 150) # or dpi = 300
```


# session information

```{r}
xfun::session_info()
```



