---
title: "Experiment 2 - Prime discrimination task"
author: "Didino Daniele"
date: "October 2021"
output: 
  html_document:
    code_folding: hide
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  echo = TRUE)
```

This file is part of the supplementary material of the manuscript:
Didino, D., Brandtner, M., & Knops, A. (2021). No influence of masked priming 
on the multiplication fact retrieval in a result verification task.

This script analyzes the Forced-choice prime detection task of experiment 2.
The analysis is based on both accuracy and d' (see function **return_d_prime** 
for the formula used to calculate it).

Dataset loaded: **exp_soa_data_PDT.csv** (data of
*forced-choice prime detection tasks* (PDT))

Load libraries and data:

```{r}
library('tidyverse')
library('here')
library('janitor')
library('plotly')
library('ggpubr')
# library('knitr')
library('kableExtra')
library('BayesFactor')

# Load my functions
source(here('funcs', 'load_my_functions.R'))

# Load data
exp2_pdt <- read_csv(here('data', 'rawdata', 'exp_soa_data_PDT.csv'))
```


Select the same participants included in the analysis on RT for the 
*result verification task*.

```{r}
exp2_pdt_sj <- 
  exp2_pdt %>% 
  filter(!(sj %in% c('sj15', 'sj17', 'sj24', 'sj28', 'sj29', 'sj31')))
```


### Plot RTs

Plot RT (across sj, accuracy and SOA)

```{r, fig.height = 6, fig.width = 9, fig.align = 'center'}
exp2_pdt_sj %>% 
  mutate(acc = as.factor(acc)) %>% 
  ggplot(data = .) +
  geom_boxplot(
    mapping = aes(x = sj, y = RT)
  ) +
  geom_point(
    mapping = aes(x = sj, y = RT, colour =  acc),
    position = position_dodge(0.9, preserve = 'total'),
    shape = 1
  ) +
  facet_wrap(~SOA, nrow = 3)
```


### Plot accuracy

Plot accuracy by SOA and subject

```{r, fig.height = 7, fig.width = 9, fig.align = 'center'}
plot_PVT <- 
  exp2_pdt_sj %>% 
  group_by(sj, SOA) %>%
  summarise(acc = mean(acc)) %>%
  ungroup() %>%
  ggplot(aes(x = acc, y = sj, colour =  SOA)) +
  geom_point(position = position_dodge(0.5, preserve = 'total')) +
  coord_cartesian(xlim = c(0, 1)) +
  geom_vline(xintercept = c(0.4, 0.5, 0.6),
             linetype = 'dashed',
             color = c('grey', 'black', 'grey'),
             size = 0.5)

ggplotly(plot_PVT)
```


Tables are created with the my function *return_info()*
```{r}
tb <- 
  return_info(exp2_pdt_sj)
```


```{r}
tb$gender
```

```{r}
tb$age
```

```{r}
tb$error
```

```{r}
tb$omitted
```

```{r}
tb$timing
```

```{r}
tb$less_200
```


Calculate statistics for accuracy (across SOA, prime type, and probe type)

```{r}
exp2_pdt_sj %>% 
  return_stats(c('SOA', 'prime_type', 'probe_type'), DV = 'acc') %>% 
  make_table('Accuracy')
```


### Analysis on accuracy 

Plot accuracy by SOA

```{r, fig.height = 6, fig.width = 7, fig.align = 'center'}
plot_acc_soa_OLD <- 
  exp2_pdt_sj %>% 
  group_by(sj, SOA) %>%
  summarise(acc = mean(acc)) %>%
  ungroup() %>% 
  ggplot(aes(x = SOA, y = acc, fill = SOA)) +
  geom_flat_violin(position = position_nudge(x = 0.1, y = 0),
                   adjust = 1.5,
                   trim = TRUE,
                   alpha = .5,
                   colour = NA) +
  geom_point(aes(x = as.numeric(factor(SOA)) - 0.15, y = acc, colour = SOA),
             position = position_jitter(width = 0.05, height = 0),
             size = 2,
             shape = 20) +
  geom_boxplot(outlier.shape = NA,
               alpha = 0.5,
               width = 0.1,
               colour = "black") +
  guides(fill = 'none') +
  guides(color = 'none') +
  scale_colour_brewer(palette = 'Dark2') +
  scale_fill_brewer(palette = 'Dark2') +
  geom_hline(yintercept = 0.5,
             linetype = 'dashed',
             color = 'red',
             size = 0.3)

plot_acc_soa_OLD
```


```{r, fig.height = 6, fig.width = 7, fig.align = 'center'}
plot_acc_soa <- 
  exp2_pdt_sj %>% 
  group_by(sj, SOA) %>%
  summarise(acc = mean(acc)) %>%
  ungroup() %>% 
  ggplot(aes(x = SOA, y = acc, fill = SOA)) +
  geom_boxplot(outlier.shape = NA,
               width = 0.2) +
  geom_point(aes(x = as.numeric(factor(SOA)) - 0.25, y = acc, colour = SOA),
             position = position_jitter(width = 0.05, height = 0),
             size = 2,
             colour = "gray40",
             shape = 20) +
  labs(x = 'SOA', y = 'Accuracy') +
  # ylim(0, 1) +
  guides(fill = 'none') +
  guides(color = 'none') +
  scale_fill_manual(values = c('gray70', 'gray70', 'gray70')) +
  scale_color_manual(values = c('gray70', 'gray70', 'gray70')) +
  theme(
    #panel.grid.major = element_blank(),
    #panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    panel.grid.major.y = element_line(colour = 'grey90'),
    panel.grid.minor.y = element_line(colour = 'grey90'),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    strip.background = element_blank(),
    text = element_text(size = 12),
    axis.text = element_text(size = 10, colour = 'black'),
    # axis.text.x = element_text(angle = 45, hjust = 1),
    # axis.title = element_text(size = 14),
    panel.border = element_rect(colour = 'black', fill = NA, size = 0.5)
  )

plot_acc_soa
```



Calculate accuracy mean by participant and SOA

```{r}
exp2_pdt_mean_acc <- 
  exp2_pdt_sj %>% 
  return_means(acc, c('sj', 'SOA'), .)
```


Compute Bayes factors

```{r}
exp2_pdt_bf <- 
  exp2_pdt_mean_acc %>% 
  group_by(SOA) %>% 
  nest() %>% 
  mutate(
    BF_test = map(data,
                   ~ttestBF(x = .x$DV,
                            mu = 0.5)),
    BF_value = map(BF_test,
                   ~extractBF(.) %>% 
                     tibble %>% 
                     select(bf, error))
  ) %>% 
  unnest(BF_value)
```


Calculate statistics for accuracy

```{r}
exp2_pdt_stats <-
  exp2_pdt_sj %>% 
  return_stats(c('SOA'), DV = 'acc')

```


### Table: accuracy and Bayes factor

Table with accuracy mean, standard deviation and standard error (aggregated on 
subject, and SOA), and Bayes factors:


```{r}
exp2_table3 <- 
  full_join(
    exp2_pdt_stats %>% 
      mutate(across(where(is.numeric), ~round(.x, digits = 3))),
    exp2_pdt_bf %>% 
      select(SOA, bf) %>% 
      rename(BF_10 = bf) %>% 
      mutate(across(where(is.numeric), ~signif(.x, 1))))

# Show results
exp2_table3 %>% 
   make_table('Accuracy and  Bayes factor (across SOA)')
```



# Calculate d' sensitivity measures

The d' is calculated for each subject and each SOA (SOA_170, SOA_120, SOA_70)

```{r}
# Calculate d'
d_prime <- 
  exp2_pdt_sj %>% 
  return_d_prime()

# Print the results in csv and txt files
d_prime %>% 
  make_table('d prime (and statistics used to calculate it) across subjects')
```

In order to have a valid d' value, the accuracy must **NOT** be 0 or 1. If 
accuracy is 0 or 1, then d' cannot be computed (in this case R output is 
"*infinite*").

The following plot report accuracy across subject, SOA and prime type (letter vs. 
number). Some subject have accuracy equal to 1 (in the plot, the *purple lines* 
represent accuracy 0 and 1), and thus d' cannot be computed.

```{r, fig.height = 7, fig.width = 9, fig.align = 'center'}
plot_PVT <- 
  exp2_pdt_sj %>% 
  group_by(sj, SOA, prime_type) %>%
  summarise(acc = mean(acc)) %>%
  ungroup() %>%
  ggplot(aes(x = acc, y = sj, colour =  SOA, shape = prime_type)) +
  geom_point(position = position_dodge(0.5, preserve = 'total')) +
  coord_cartesian(xlim = c(0, 1)) +
  geom_vline(xintercept = c(0, 1),
             linetype = 'dashed',
             color = 'purple',
             size = 0.3)

ggplotly(plot_PVT)
```


The d' can be computed in all SOA conditions only for the following subjects:
1, 3, 4, 7, 10, 13, 14, 18, 19, 26, 33

```{r}
# Check whether d' values is infinite or NA
sj_excluded <- 
  d_prime %>% 
  filter(is.infinite(d_prime) | is.na(d_prime)) %>%  
  pull(sj) %>% 
  unique()

# Subject excluded: sj03, sj06, sj13, sj14, sj15, sj16, sj28
sj_excluded

# Subject selected: sj03, sj06, sj13, sj14, sj15, sj16, sj28
setdiff(unique(d_prime$sj), sj_excluded)
```


Select subjects with finite d' values.

```{r}
# exclude sj with infinite d'
d_prime_f <- 
  d_prime %>% 
  filter(!(sj %in% sj_excluded))
```


Statistics for d'

```{r}
# Calculate mean d'
t_mean_d_prime <- 
  d_prime_f %>%
  return_stats(., c('SOA'), DV = 'd_prime')

# Show the table with the statistics
t_mean_d_prime %>%
  make_table('d prime statistics')
```


Plot d prime by SOA

```{r, fig.height = 6, fig.width = 8, fig.align = 'center'}
d_prime_f %>% 
  ggplot(aes(x = SOA, y = d_prime, fill = SOA)) +
  geom_flat_violin(aes(fill = SOA),
                   position = position_nudge(x = .1, y = 0),
                   adjust = 1.5,
                   trim = FALSE,
                   alpha = .5,
                   colour = NA) +
  geom_point(aes(x = as.numeric(factor(SOA)) - .15, y = d_prime, colour = SOA),
             position = position_jitter(width = .05),
             size = 2,
             shape = 20) +
  geom_boxplot(aes(x = SOA, y = d_prime, fill = SOA),
               outlier.shape = NA,
               alpha = .5,
               width = .1,
               colour = "black") +
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  geom_hline(yintercept = 0,
             linetype = 'dashed',
             color = 'red',
             size = 0.5)
```

### Conclusions

Despite the masking, both accuracy and d' clearly show that participants could 
perceive the prime.


# Save plots in a file

```{r, fig.show='hide'}
ggarrange(plot_acc_soa)
ggsave(here('figures', 'exp2_PDT_acc.tiff'),
       width = 4,
       height = 3,
       dpi = 150) # or dpi = 300
```


# session information

```{r}
xfun::session_info()
```



