---
title: 'Experiment 2 - analysis delta RTs'
author: 'Didino Daniele'
date: 'October 2021'
output: 
  html_document:
    code_folding: hide
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(
  comment = '#>',
  collapse = TRUE,
  echo = TRUE)
```

This file is part of the supplementary material of the manuscript:
Didino, D., Brandtner, M., & Knops, A. (2021). No influence of masked priming 
on the multiplication fact retrieval in a result verification task.

This script reports the analysis for experiment 2.

Dataset loaded: **exp2_data.rds** (data of *result verification task*)

Load libraries, my functions (**my_functions** folder) and data 
(**data/processed** folder):

```{r}
library('ggpubr')
library('here')
library('kableExtra')
# library('knitr')
library('plotly')
library('ggridges')
library('tidyverse')
library('BayesFactor')

# Load my functions
source(here('funcs', 'load_my_functions.R'))

# Load data
exp2 <- readRDS(here('data', 'processed', 'exp2_data.rds'))
```


Exclude outliers

```{r}
exp2 <- 
  exp2 %>% 
  filter(outlier == FALSE)
```

# Calculate delta RTs

```{r}
exp2_dRT <- 
  exp2 %>% 
  return_delta_RT(.,
                  y_col = RT,
                  cols_to_group = c('sj', 'problem_size', 'SOA'),
                  cols_to_subtract = c('prime_cond'),
                  neutral_cond = 'neutral')
```


# Delta RTs versus RTs

```{r, fig.height = 4, fig.width = 7, fig.align = 'center'}
dens_RT <- 
  ggplot(exp2, aes(RT)) + 
  geom_density() +
  stat_function(fun = dnorm, 
                args = list(mean = mean(exp2$RT), sd = sd(exp2$RT)),
                color = 'blue') +
      ggtitle('')


dens_dRT <- 
  ggplot(exp2_dRT, aes(dRT)) + 
  geom_density() +
  stat_function(fun = dnorm, 
                args = list(mean = mean(exp2_dRT$dRT), sd = sd(exp2_dRT$dRT)),
                color = 'blue') +
      ggtitle('')
  
ggarrange(dens_RT,
          dens_dRT,
          ncol = 2,
          nrow = 1,
          labels = c('RT', 'delta RT'))
```


# Delta RTs table

Table with RTs mean, standard deviation and standard error (aggregated on 
                                                            subject and condition):

```{r}
# Calculate statistics
exp2_stats <- 
  exp2_dRT %>%
  return_stats(c('problem_size', 'SOA', 'cond'),
               DV = 'dRT')

# Show results
exp2_stats %>% 
  make_table('Statistics (prime condition by problem size)')
```


# Delta RTs plots

RTs distribution across prime conditions:

```{r, fig.height = 6, fig.width = 8, fig.align = 'center'}
plot_1 <-
  exp2_dRT %>% 
  ggplot(aes(dRT, fill = cond)) +
  geom_density(alpha = 0.6) +
  facet_wrap(~ SOA + problem_size, ncol = 2) +
  theme(panel.spacing = unit(2, "cm"))

ggplotly(plot_1)
```


```{r, fig.height = 6, fig.width = 8, fig.align = 'center'}
exp2_dRT %>% 
  ggplot(aes(x = dRT, y = cond, fill = stat(x))) +
  geom_density_ridges_gradient(scale = 3) +
  scale_fill_viridis_c(name = 'RTs', option = 'C') +
  labs(y = 'Prime condition') +
  facet_wrap(~ SOA + problem_size, ncol = 2) 
```


# Bayes factor

Bayes factors are computer with the package **BayesFactor**.


```{r}
tribble(
  ~BF,      ~Evidence,
  '0-3',    'Anectodal',
  '3-10',   'Moderate',
  '10-30',  'Strong',
  '30-100', 'Very_strong',
  '>100',   'Decisive') %>% 
  make_table('Bayes factor interpretation')
```



```{r}
exp2_bf <- 
  exp2_dRT %>% 
  group_by(problem_size, SOA, cond) %>% 
  nest() %>% 
  mutate(
    # "DV" is the column with the means returned by "return_means()"
    BF_test = map(data,
                  ~ttestBF(x = .$dRT,
                           mu = 0)),
    BF_value = map(BF_test,
                   ~extractBF(.) %>% 
                     tibble %>% 
                     select(bf, error))
  ) %>% 
  unnest(BF_value)

exp2_bf

exp2_bf <- 
  exp2_bf %>%
  select(problem_size, SOA, cond, bf) %>% 
  rename(BF_10 = bf) %>% 
  mutate(
    BF_01 = 1 / BF_10
  ) 

# Show results
exp2_bf %>% 
  make_table('Bayes factor')
```


# Plot dRT against mean RT (by subject)


Create a single data frame with dRT and mean RT (a data point for each
subject, problem size and prime condition)

```{r}
# Mean RT by subject
exp2_meanRT_sj <- 
  exp2 %>%
  return_stats(c('sj', 'problem_size', 'SOA', 'cond'),
               DV = 'RT') %>% 
  select(sj, problem_size, SOA, prime_cond, Mean) %>% 
  rename(cond = prime_cond) %>% 
  filter(cond != 'neutral')

# Join data frames
exp2_dRT_meanRT <- 
  full_join(exp2_dRT,
            exp2_meanRT_sj,
            by = c('sj', 'problem_size', 'SOA', 'cond'))
```


Plot for large problems

```{r, fig.height = 8, fig.width = 8, fig.align = 'center'}
exp2_dRT_meanRT %>% 
  filter(problem_size == 'large') %>% 
  ggplot(aes(Mean, dRT)) +
  geom_point() +
  geom_hline(yintercept = 0,
             linetype = 'dashed',
             color = 'red',
             size = 0.5) +
  facet_wrap(~ cond + SOA, ncol = 3)
```



Plot for small problems

```{r, fig.height = 8, fig.width = 8, fig.align = 'center'}
exp2_dRT_meanRT %>% 
  filter(problem_size == 'small') %>% 
  ggplot(aes(Mean, dRT)) +
  geom_point() +
  geom_hline(yintercept = 0,
             linetype = 'dashed',
             color = 'red',
             size = 0.5) +
  facet_wrap(~ cond + SOA, ncol = 3)
```


# session information

```{r}
xfun::session_info()
```

