---
title: "Experiment 3 - preprocessing"
author: "Didino Daniele"
date: "October 2021"
output: 
  html_document:
    code_folding: hide
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  echo = TRUE)
```

This file is part of the supplementary material of the manuscript:
Didino, D., Brandtner, M., & Knops, A. (2021). No influence of masked priming 
on the multiplication fact retrieval in a result verification task.

This script run the data pre-processing of experiment 3.

Dataset loaded: **exp_soa_2_data.csv** (data of *result verification task*)

Load libraries and data:

```{r}
library('tidyverse')
library('here')
library('janitor')
library('plotly')
# library('knitr')
library('kableExtra')

# Load my functions
source(here('funcs', 'load_my_functions.R'))

# Load data (included )
exp3_rowData <- read_csv(here('data', 'rawdata', 'exp_soa_2_data.csv'))
```


### Evaluate accuracy

Plot accuracy by subject

```{r, fig.height = 6, fig.width = 8, fig.align = 'center'}
plot_acc_sj <-
  exp3_rowData %>%
  group_by(sj) %>%
  summarise(acc = mean(acc)) %>%
  ggplot(aes(x = acc, y = sj)) +
  geom_point() +
  coord_cartesian(xlim = c(0, 1)) +
  geom_vline(xintercept = 0.75,
             linetype = 'dashed',
             color = 'red',
             size = 1)

ggplotly(plot_acc_sj)
```


Plot accuracy by block and subject

```{r, fig.height = 4, fig.width = 8, fig.align = 'center'}
plot_acc_block_sj <- 
  exp3_rowData %>% 
  group_by(sj, block) %>% 
  summarise(acc = mean(acc)) %>% 
  ungroup() %>% 
  ggplot(aes(x = block, y = acc, group = sj, colour = sj)) +
  geom_line() +
  coord_cartesian(ylim = c(0, 1)) +
  scale_x_discrete(limits = factor(1:10)) +
  geom_hline(yintercept = 0.75,
             linetype = 'dashed',
             color = 'red',
             size = 1)

ggplotly(plot_acc_block_sj)
```

### Evaluate RTs

Plot RTs by subject

```{r, fig.height = 4, fig.width = 8, fig.align = 'center'}
plot_RT_sj <-
  exp3_rowData %>% 
  filter(acc == 1) %>% 
  group_by(sj) %>%
  ggplot(aes(x = sj, y = RT)) +
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75))

ggplotly(plot_RT_sj)
```

Plot RT by block and subject

```{r, fig.height = 4, fig.width = 8, fig.align = 'center'}
plot_RTs_block_sj <- 
  exp3_rowData %>% 
  filter(acc == 1) %>% 
  group_by(sj, block) %>% 
  summarise(RT = mean(RT)) %>% 
  ggplot(aes(x = block, y = RT, group = sj, colour = sj)) +
  geom_line() +
  scale_x_discrete(limits = factor(1:10))

ggplotly(plot_RTs_block_sj)
```

### Select participants and trials

Excluded participants:

* **SJ 27** has low accuracy (about 50%) in block 5.


```{r}
exp3_excludedSJ <- 
  exp3_rowData %>% 
  filter(!(sj %in% c('sj27')))
```


Removed trials:
  
* Filler trials
* Incorrect equation trials (where the proposed result is not the product)

```{r}
# filler: 0 = experimental trial, 1 = filler trial
exp3_no_filler <- 
  exp3_excludedSJ %>% 
  filter(filler == 0 & probe_type == 'product')
```

Problems selected for the analysis:

```{r}
exp3_no_filler %>% 
  select('op1', 'op2') %>% 
  table %>%
  make_table('Problems selected')
```


### Accuracy by conditions

Table with accuracy mean, standard deviation and standard error (aggregated on
subject and condition)

```{r}
# Calculate statistics for accuracy
exp3_stats_acc <- 
  exp3_no_filler %>%
  return_stats(c('SOA', 'problem_size', 'prime_cond'), DV = 'acc')

exp3_stats_acc %>% 
   make_table('Accuracy by problem_size and prime_cond')
```


### Tables with demographics and performance

Tables are created with the my function *return_info()*
```{r}
tb <- 
  return_info(exp3_no_filler)
```

```{r}
tb$gender
```

```{r}
tb$age
```

```{r}
tb$error
```

```{r}
tb$omitted
```

```{r}
tb$timing
```

```{r}
tb$less_200
```


### Exclude trials
Exclude trials with omitted answer, errors, RT less than 200 ms, and wrong timing (wrong
stimuli onset/offset)

```{r}
# Exclude omitted, errors, RT < 200 ms, and wrong timing
exp3_correct_ans <- 
  exp3_no_filler %>% 
  filter((acc == 1) & (RT > 200) & (timing == 'ok'))
```


### Outliers

For each participant, trials more than **2.5 standard deviations** from
the mean are classified as outliers and excluded from the frequentist
analysis. 


```{r, fig.height = 4, fig.width = 8, fig.align = 'center'}
# identify outlier

threshold = 2.5

exp3_rt_outlier <- 
  exp3_correct_ans %>%
  group_by(sj) %>% 
  mutate(outlier = !between(
    RT,
    mean(RT) - (threshold * sd(RT)),
    mean(RT) + (threshold * sd(RT))
  )) %>% 
  ungroup()


# percentage outliers

exp3_rt_outlier %>% 
  summarise(
    N_outlier = sum(outlier == TRUE),
    N_trial = length(outlier)
  ) %>% 
  mutate(percent_outlier = N_outlier / N_trial * 100) %>% 
  make_table('Outliers')
```


Plot the trials classified as outliers

```{r, fig.height = 4, fig.width = 9, fig.align = 'center'}
plot_outlier <- 
  ggplot(data = exp3_rt_outlier) +
  geom_boxplot(aes(x = sj, y = RT)) +
  geom_point(aes(x = sj, y = RT, colour =  outlier),
             position = position_dodge(0.9, preserve = 'total'),
             shape = 20,
             size = 0.5) +
  theme(axis.text.x = element_text(angle = 50, vjust = 1, hjust = 1))

ggplotly(plot_outlier)
```


### Save processed data

The processed data are saved in the file **data/processed/exp3_data.rds**.

```{r}
saveRDS(
  object = exp3_rt_outlier,
  file = here('data', 'processed', 'exp3_data.rds'))
```


# session information

```{r}
xfun::session_info()
```
